---
title: "Summary Tabular Data Homework"
format: html
editor: visual

#refer to ReadMeAmerifluxdata txt file
#refer to Rodney Dyer's Tidyverse powerpoint
---

## Abstract
Ameriflux FASET data

## Introduction
Ameriflux flux towers are widespread in all the United States. They are eddy covariance towers
Below, data from FASET (Forest Accelerated Succession ExperimenT) up in Michigan at the University of Michigan Biological Station is being summarized.
The background to FASET is that it is a 

## Methods

1. imported csv files and read them
```{r}
file <-"docs/AMF_US-UMd_FLUXNET_FULLSET_YY_2007-2021_3-5.csv"
ameriflux <- read_csv(file)
names(ameriflux)
```

2. Specified which column numbers I'll be looking at (interested in the following variables:NEE_CUT_REF, TA_F and PPFD_IN)
```{r}
hw2data <- ameriflux[ c(56,15,104)]
summary(hw2data)
```

3. Need to cut out the -9999.0 values because they are not actual readings
```{r}
ameriflux [ c(56,15,104)] |> 
  filter( PPFD_IN > -9999.0 ) -> newtable
summary(newtable)
```

4. Because Ameriflux data is mostly already processed, I think all I need to do is to 

## Results
